In this supplement, we will provide a full walk-through of the examples given
in \cref{btdde:sec:Examples} with the open source bifurcation software package
\DDEBIFTOOL\footnote{\url{http://ddebiftool.sourceforge.net/}}
\cite{2014arXiv1406.7144S}. Additionally, the Julia code, used for the
numerical simulation, with the package {\tt
DifferentialEquations.jl}\footnote{\url{https://github.com/SciML/DifferentialEquations.jl}}
\cite{rackauckas2017differentialequations} is shown. This allows other researchers to replicate the findings in the main text fully. The given code can easily be modified to study other DDE models undergoing generic or transcritical Bogdanov-Takens bifurcations. While studying these models, some new results were
obtained.

The code in this supplement has also been included into the \DDEBIFTOOL package on the source-forge repository and can be executed without the need to copy and paste. In this supplement, we mainly focus on the initialization and continuation of the various codimension one equilibrium and homoclinic bifurcation curves emanating from the Bogdanov--Takens points and on numerical simulation near the bifurcation points. The online tutorials, as well as the manual and its references, provide a comprehensive overview of \DDEBIFTOOL's capabilities and functionality.

Note that reading this supplement may feel, at times, somewhat repetitive. We see
this as a positive sign. Indeed, our predictors need little to none adjustment
before starting continuation of the codimension one curves emanating from the
generic and transcritical Bogdanov--Takens bifurcation.

To follow the examples below, we recommend using the \DDEBIFTOOL package
supplied with the article. Also, note that the \MATLAB code has been tested on 
\MATLAB 2020b and \OCTAVE 6.4.0 using \OCTAVE symbolic
package version 2.9.0. Different results may occur on other versions of 
\MATLAB or \OCTAVE.

